timesliced_random_cell_selection

### 2018-11-07 src/timesliced_random_cell_selection.Rmd
NAFO region addition to background points

save as csv
```{r}
write.csv(adddata_aea, file = "../output/bio/data_aea.csv", row.names = FALSE)

>>>>

change name of long lat columns to decimalLongitude and decimalLatitude respectively
```{r}
sp_background <- as.data.frame(sp_background) #need to go back to a 'normal' dataframe to change col names
head(sp_background) #note the columns in question have changed name...
colnames(sp_background)[colnames(sp_background)=="longitude.1"] <- "decimalLongitude"
colnames(sp_background)[colnames(sp_background)=="latitude.1"] <- "decimalLatitude"
head(sp_background)
```

save as csv
```{r}
write.csv(sp_background, file = "../output/bio/background_all_lonlat.csv", row.names = FALSE)
```

# Add NAFO Region background point is in
NAFO Zones shapefile obtained from [NAFO](https://www.nafo.int/Data/GIS)

```{r NAFO shapefile extraction}
library(rgdal)
library(sp)
coordinates(sp_background) <- c("decimalLongitude", "decimalLatitude") 
nafo_zones <- readOGR(dsn=path.expand("../data/bio/nafo_zones"), layer = "nafo_zones_wgs84") #this loads the shapefile
proj4string(sp_background) <- proj4string(nafo_zones) #tells R that the occurrence data is the same projection as the shapefile
sp_background$nafo_zone <- over(sp_background, nafo_zones)$ZONE #ZONE is where the zone data is held in teh shapefiles' attributes
head(sp_background) #just to check it worked
```

Great. Lets see if any are missing a NAFO Zone. But first, write to a csv and reload as the data is now some wierd 'spatial points dataframe'...
```{r}
write.csv(sp_background, "../output/bio/background_all_lonlat_nafo.csv", row.names=FALSE)
sp_background <- as.data.frame(sp_background) 
bc_nafo_na <- subset(sp_background, is.na(sp_background$nafo_zone))
bc_nafo_na
```
ok lots don't have a NAFO region attached. This is probably the Hudson Bay issue again...

Uh oh there is a lot. A bet a bunch of them are in the Hudson Strait (which is outside the NAFO Zone).Map the nafo_na points...
```{r}
plot(map2, xlim = c(-65, -40), ylim =c(30, 70), asp = 1, main = "Occurences missing a NAFO Zone", col = "cornsilk") #the x and y lim are the long-lat bounds of the map
points(bc_nafo_na$decimalLongitude, bc_nafo_na$decimalLatitude, col = "red") #this adds points to the mapet", xlab = "Longitude", ylab = "Latitude")
```

huh that is interesting... I think I want to plot this in Arc and take a closer look...
